---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# isoraster

<!-- badges: start -->
<!-- badges: end -->

The goal of isoraster is to create contour lines and contour polygons from rasters. 

The R terra package is used as a foundation. The R isoband package is the engine, sf is used as an intermediate format internally. 

## Installation

You can install the development version of isoraster like so:

``` r
remotes::install_github("mdsumner/isoraster")
```

## Example

This is a basic example. 

```{r example}
library(isoraster)
plot(isoband_terra(rast(volcano)))

plot(isoband_terra(rast(volcano), seq(100, 170, by = 5)))

plot(isoband_terra(rast(volcano), c(100, 110, 120), c(110, 120, 130)))

```


## Code of Conduct
  
Please note that the isoraster project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
